Late Fusion via Subspace Search with Consistency Preservation

### 2017-03-02 egpaper_for_review.tex
iccv v1.1

%背景 多model融合
Feature representation of objects, which transforms raw data into numerical features, is a prerequisite for most real-world applications.
There are often multiple ways to generate numerical features from raw data for visual recognition.
For example, for image data, one can construct hand-crafted features such as scale-invariant feature transform
(SIFT) feature~\cite{loweijcv2004distinctive} and Histograms of Gradients (HOG) feature~\cite{dalalcvpr2005histograms},
or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevsky2012imagenet}.
Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
Each category of features tends to capture some specific characteristics of data,
such as textures of images and frequencies of text data.
When building a prediction model, the model trained on one kind of feautures could be biased and hence may incur unsatisfactory performance.
Existing works have investigated the performance improvement by combining multiple kinds of features in real-world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.

%% late fusion is a common sigle model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

@@

To prevent from the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
As for outlier detection,
we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
Due to the fact that the $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction,
we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the nonsmooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.

The main contributions of this work are summarized as below:
\begin{itemize}
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss. 
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

MKL based method is a simple but efficient way to combine different features for multi-model fusion,
and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel.
In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values,
which learns the weights, thresholding and smoothing parameters in a joint framework.
However, all these mkl based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

Some other fusion algorithms are propsed for specific tasks, which would be hard to extend to general problems.
In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features impove the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.

@@

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as below:
{\small
\begin{align}\label{eq:l12_mf}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a nonsmooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

@@

Most existing matrix factorization optimization methods only consider smooth loss functions, rather than the nonsmooth $\ell_{1,2}$ loss used in Problem~(\ref{eq:l12_mf}).
In this section, we present an ALM based algorithm to optimize Problem~(\ref{eq:l12_mf}).

@@

\begin{theorem}
\label{theorem:alm_convergence}
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
  and $\{\blambda_k\}$ is bounded. Any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}

@@

The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
In other words, we search the solution for $\bX$ in a low-rank subspace.
Let $r$ be a known scalar.
A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
{\small
\begin{align}
\M_{r} &=& \{\bX\in \R^{n\times m\calC}: \rank(\bX) = r\} \nonumber \\
       &=& \{\U\diag(\bsigma)\V^{\trsp}: \U \in \textrm{St}_{r}^{n}, \V \in
           \textrm{St}_{r}^{m\calC}, ||\bsigma||_0 = r\} \nonumber
\end{align}
}
\noindent
where $\textrm{St}_{r}^{n} = \{\U \in \R^{n\times r}:
\U^{\trsp}\U = \I \}$ dentoes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
We denote the tangent space by $T_{\bX}\M_{r}$ of $\M_{r}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
which is obtained as below
{\small
\begin{align}
\label{eq:tangent_vector}
&&T_{\bX}\M_{r} =  \{\U\bM\V^{\trsp} \!\!+\! \U_p\V^{\trsp} \!\!+\!
\U\V_p^{\trsp}: \bM \in \R^{r\times r}, \nonumber\\ && \U_p \in \R^{n\times r},
\U_p^{\trsp}\U = \0, \V_p \in \R^{m\calC \times r}, \V_p^{\trsp}\V = \0\}.
\end{align}
}
\noindent
One can define a metric $g_{\bX}({\bA},{\bB}) = \langle{\bA},{\bB}\rangle$ on $\M_{r}$,
with $\bX \in \M_{r}$ and ${\bA},{\bB} \in T_{\bX}\M_{r}$,
then $\M_{r}$ becomes a Riemannian manifold by restricting
$\langle\bA,\bB\rangle$
to the \emph{tangent bundle}, defined as the disjoint union of all tangent spaces:
$T\M_{r} = \bigcup_{\bX\in \M_{r}}\{\bX\} \times T_{\bX}\M_{r}
         = \! \{(\bX,\bP)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \bP \in T_{\bX}\M_{r}\}.$

@@

Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
{\small
\begin{align}
\label{eq:subproblem_wrt_E_1}
  \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bN = \bL - \bX + \frac{\blambda}{\mu}$.
We thus obtain the subproblem \wrt. $\bE$ as below:
{\small
\begin{align}
\label{eq:subproblem_wrt_E_2}
  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
\end{align}
}
\noindent
The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
{\small
\begin{align}\label{eq:column_wise_soft_thresholding}
  \bE_{i} = \calS_{\alpha}(\bN_{i}) = \left\{
    \begin{aligned}
      & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
      & \bN_{i} - \frac{\alpha \bN_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
    \end{aligned}
    \right.
\end{align}
}
\noindent
where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bN$,
%and $\alpha = \frac{2}{\mu}$.
and $\alpha = \frac{1}{2}$.

\subsection{Post Process}
As we recover the low-rank matrix $\bX$ from the label assignment matrix $\bL$,
it needs a post process to generate the prediction label for each testing data.
Intuitively, there might be several possible ways to select as below:
\begin{itemize}
  \item \textbf{[AVE].} A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
    The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
  \item \textbf{[VOTE].} For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ as the index of the highest value in the $i$-th row of $\bX_j$.
      Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
      Finally, we choose the label with the most votes to be the prediction results.
  \item \textbf{[GATE].} $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
      As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
      The similar process as the first strategy is applied to the above results, which predictes the final labels.
\end{itemize}
According to the experiments, the last strategy ``GATE'' outperforms than the others.
So We choose the last one as the post process for our fusion method and analyse inner reasons during the experiment section.

@@

Now we analyze the computation complexity of our proposed algorithm.
The sub-algorithm in Section~3.3 solve the solution of $\bX$.
The primary computation is described in Algorithms.~\ref{alg:compute_riemannian_grad} and~\ref{alg:LRGeomCG},
which uses subspace search to optimize the solution.
And the complexity is $T \times O((n+{\calC}m){\calC}^2)$, where $T$ is the number of iterations.
According to \cite{vandereyckensiamjo2013low}, $T$ is less than 100 for most situations,
and more details can be found in \cite{vandereyckensiamjo2013low}.
The complexity of optimization on $\bE$ and post-processing can be easily calculated as $O(nm{\calC})$ and $O(nm{\calC})$.
So, the total comlexity per iteration is $T \times O((n+{\calC}m){\calC}^2) + O(nm{\calC})$,
which is linear by growing of $n$ and $m$, with the cubic complexity of $\calC$.

Comparing with those nuclear norm based methods~\cite{gaoijcai2016robust,ye2012robust} whose computational complexity is cubic due to the presence of SVDs,
our algorithm is more efficient for large scale problems.
For example, \cite{gaoijcai2016robust} reportes their entire complexity is $(m{\calC})^3+n(m{\calC})^2$ per iteration.
With the increase in the number of classifers,
the computation costs too much to be affordable due to the cubic complexiry of $m$,
but ours are able to solve the solution.

@@

In this section, we first visualize the results of our approach on the synthetic dataset.
Then we evaluate the perfomance on eight publicly available real-world data sets,
UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
The strategy analysis for post process is detailed in the last subsection.

%Details on feature extraction for each dataset are described in the second subsection.
%, and the confidence scores are set as outputs of LIBLINEAR.
%Then we put the confidence scores as the input X of our alogrithm.

Five state-of-the-art fusion methods are compared with our proposed alogrithm :
\begin{itemize}
\item Average Score Fusion(ASF). we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization.
\item Multiple Kernel Learning (MKL).  MKL learns a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$. We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} toolbox to train our MKL model.
\item Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}.
The core alogrithm in RCEC can be modified to recover $\bX$ from $L$ in Problem.~\ref{eq:l12_mf}, and the post process is same as our method.
\item Feature Weighting via Optimal Thresholding (FWOT) \cite{xuiccv2013feature}.
The authors propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
\item LPBoost~\cite{gehler2009feature}. In this method, a variant linear combination is applied to multiple classifiers to boost performance.
\end{itemize}

@@

In CIFAR-10 dataset, totally 60000 32x32 colour pictures are categoried into 10 classes, with 6000 pictures per class.
There are 50000 training data and 10000 testing data.
Fourteen CNN features are extracted from multiple state of the art models.
This experiments exhibit the ability of our algorithm to handle large scale data.

>>>>

%背景 多model融合
Feature representation of objects, which transforms raw data into numerical features, is a prerequisite for most real-world applications.
There are often multiple ways to generate numerical features from raw data for visual recognition.
For example, for image data, one can construct hand-crafted features such as scale-invariant feature transform
(SIFT) feature~\cite{loweijcv2004distinctive} and Histograms of Gradients (HOG) feature~\cite{dalalcvpr2005histograms},
or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevsky2012imagenet}.
Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
Each category of features tends to capture some specific characteristics of data,
such as textures of images and frequencies of text data.
When building a prediction model, the model trained on one kind of features could be biased and hence may incur unsatisfactory performance.
Existing works have investigated the performance improvement by combining multiple kinds of features in real-world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.

%% late fusion is a common single model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

@@

To prevent from the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
As for outlier detection,
we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
However, the single $L_2$ doesn't have the ability to detect outliers and the single $L_1$ has the instability property.
Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

The main contributions of this work are summarized as below:
\begin{itemize}
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to non-smooth $\ell_{1,2}$ loss. 
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

MKL based method is a simple but efficient way to combine different features for multi-model fusion,
and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel.
In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values,
which learns the weights, thresholding and smoothing parameters in a joint framework.
However, all these MKL based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method can not be guaranteed to converge the global solution in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.

Some other fusion algorithms are proposed for specific tasks, which would be hard to extend to general problems.
In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.

@@

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as below:
{\small
\begin{align}\label{eq:l12_mf}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

@@

Most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth $\ell_{1,2}$ loss used in Problem~(\ref{eq:l12_mf}).
In this section, we present an ALM based algorithm to optimize Problem~(\ref{eq:l12_mf}).

@@

The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
We proof the convergence of ALM for solving a non-convex problem relying on the gradient, as following:

\begin{theorem}
\label{theorem:alm_convergence}
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
  and $\{\blambda_k\}$ is bounded.
  As $k \to \infty$, the gradient of $\calL$ vanishes,
  thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}

@@

The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
In other words, we search the solution for $\bX$ in a low-rank subspace.
Let $r$ be a known scalar.
A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
{\small
\begin{align}
\M_{r} &=& \{\bX\in \R^{n\times m\calC}: \rank(\bX) = r\} \nonumber \\
       &=& \{\U\diag(\bsigma)\V^{\trsp}: \U \in \textrm{St}_{r}^{n}, \V \in
           \textrm{St}_{r}^{m\calC}, ||\bsigma||_0 = r\} \nonumber
\end{align}
}
\noindent
where $\textrm{St}_{r}^{n} = \{\U \in \R^{n\times r}:
\U^{\trsp}\U = \I \}$ denotes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
We denote the tangent space by $T_{\bX}\M_{r}$ of $\M_{r}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
which is obtained as below
{\small
\begin{align}
\label{eq:tangent_vector}
&&T_{\bX}\M_{r} =  \{\U\bM\V^{\trsp} \!\!+\! \U_p\V^{\trsp} \!\!+\!
\U\V_p^{\trsp}: \bM \in \R^{r\times r}, \nonumber\\ && \U_p \in \R^{n\times r},
\U_p^{\trsp}\U = \0, \V_p \in \R^{m\calC \times r}, \V_p^{\trsp}\V = \0\}.
\end{align}
}
\noindent
One can define a metric $g_{\bX}({\bA},{\bB}) = \langle{\bA},{\bB}\rangle$ on $\M_{r}$,
with $\bX \in \M_{r}$ and ${\bA},{\bB} \in T_{\bX}\M_{r}$,
then $\M_{r}$ becomes a Riemannian manifold by restricting
$\langle\bA,\bB\rangle$
to the \emph{tangent bundle}, defined as the disjoint union of all tangent spaces:
$T\M_{r} = \bigcup_{\bX\in \M_{r}}\{\bX\} \times T_{\bX}\M_{r}
         = \! \{(\bX,\bP)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \bP \in T_{\bX}\M_{r}\}.$

@@

Similarly, to update $\bE$, we consider the augmented Lagrangian function \wrt. $\bE$ as below:
{\small
\begin{align}
\label{eq:subproblem_wrt_E_1}
  \calL (\bE) = & || \bE ||_{1,2} + || \bN - \bE ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bN = \bL - \bX + \frac{\blambda}{\mu}$.
We thus obtain the subproblem \wrt. $\bE$ as below:
{\small
\begin{align}
\label{eq:subproblem_wrt_E_2}
  \min_{\bE} & || \bE ||_{1,2} + || \bN - \bE ||_F^2 .
\end{align}
}
\noindent
The above problem can be efficiently solved by the following column-wise soft-thresholding operator~\cite{xiao2015FaLRR}:
{\small
\begin{align}\label{eq:column_wise_soft_thresholding}
  \bE_{i} = \calS_{\alpha}(\bN_{i}) = \left\{
    \begin{aligned}
      & \zerocolumn,~\text{if}~ ||\bN_{i}||_2 \leq \alpha   \\
      & \bN_{i} - \frac{\alpha \bN_{i}}{|| \bN_{i} ||_2},~\text{otherwise,}
    \end{aligned}
    \right.
\end{align}
}
\noindent
where $\bE_{i}$ and $\bN_{i}$ denote the $i$-th column of $\bE$ and $\bN$,
and $\alpha = \frac{1}{2}$.

\subsection{Post Process}
As we recover the low-rank matrix $\bX$ from the label assignment matrix $\bL$,
it needs a post process to generate the prediction label for each testing data.
Intuitively, there might be several possible ways to select as below:
\begin{itemize}
  \item \textbf{[AVE].} A prediction score matrix $\bX^{*} \in \dsR^{n \times {\calC}}$ is obtained by averaging $[ \bX_1, \bX_2, ..., \bX_{\calC}]$.
    The indicator of the highest value in each row of $\bX^{*}$ is regard as the predicted label for the corresponding data.
  \item \textbf{[VOTE].} For $\bX_j$ where $1 \leq j \leq m$, we set $\bI_{ij}$ as the index of the highest value in the $i$-th row of $\bX_j$.
      Each $\bI_{ij}$ contributes one point to the $i$-th data with label $\bI_{ij}$.
      Finally, we choose the label with the most votes to be the prediction results.
  \item \textbf{[GATE].} $\bX_j$ where $1 \leq j \leq m$ are transformed through softmax function as a gate of the corresponding confidence score matrix, which is normalized by $L_2$ norm.
      As $\bX_j$ contains outlier rejection information, we product the $\bX_j$ by the corresponding score matrix after softmax and normalization.
      The similar process as the first strategy is applied to the above results, which predicts the final labels.
\end{itemize}
According to the experiments, the last strategy ``GATE'' outperforms than the others.
So We choose the last one as the post process for our fusion method and analyze inner reasons during the experiment section.

@@

Now we analyze the computation complexity of our proposed algorithm.
The sub-algorithm in Section~3.3 solve the solution of $\bX$.
The primary computation is described in Algorithms.~\ref{alg:compute_riemannian_grad} and~\ref{alg:LRGeomCG},
which uses subspace search to optimize the solution.
And the complexity is $T \times O((n+{\calC}m){\calC}^2)$, where $T$ is the number of iterations.
According to \cite{vandereycken2013lowrank}, $T$ is less than 100 for most situations,
and more details can be found in \cite{vandereycken2013lowrank}.
The complexity of optimization on $\bE$ and post-processing can be easily calculated as $O(nm{\calC})$ and $O(nm{\calC})$.
So, the total complexity per iteration is $T \times O((n+{\calC}m){\calC}^2) + O(nm{\calC})$,
which is linear by growing of $n$ and $m$, with the cubic complexity of $\calC$.

Comparing with those nuclear norm based methods~\cite{gaoijcai2016robust,ye2012robust} whose computational complexity is cubic due to the presence of SVDs,
our algorithm is more efficient for large scale problems.
For example, \cite{gaoijcai2016robust} reportes their entire complexity is $(m{\calC})^3+n(m{\calC})^2$ per iteration.
With the increase in the number of classifiers,
the computation costs too much to be affordable due to the cubic complexity of $m$,
but ours are able to solve the solution.

@@

In this section, we first visualize the results of our approach on the synthetic dataset.
Then we evaluate the performance on eight publicly available real-world data sets,
UCF101~\cite{soomro2012ucf101}, CIFAR-10~\cite{krizhevsky2009learning}, CIFAR-100~\cite{krizhevsky2009learning}, Oxford-IIIT-Pet~\cite{parkhi2012cats}, PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flower 17~\cite{nilsback2006visual}, Pascal Sentence~\cite{rashtchian2010collecting} and Wikipedia~\cite{rasiwasia2010new}.
The strategy analysis for post process is detailed in the last subsection.

Five state-of-the-art fusion methods are compared with our proposed algorithm :
\begin{itemize}
\item Average Score Fusion(ASF). we directly average the confidence scores predicted by classifiers. We use $L_2$ norm on each classifier's results for normalization.
\item Multiple Kernel Learning (MKL).  MKL learns a weight w for each classifiers, the final score are obtained from function $f(s)=w^{T}s, \sum w = 1$. We use liblinear-mkl\footnote{\url{http://www.csie.ntu.edu.tw/~b95028/software/liblinear-mkl/}} toolbox to train our MKL model.
\item Robust Convex Ensemble Clustering (RCEC)\cite{gaoijcai2016robust}.
The core alogrithm in RCEC can be modified to recover $\bX$ from $L$ in Problem.~\ref{eq:l12_mf}, and the post process is same as our method.
\item Feature Weighting via Optimal Thresholding (FWOT) \cite{xuiccv2013feature}.
The authors propse a method to learn thresholding, smoothing parameters and weights in a joint framework to combine prediction confidence scores of different features.
\item LPBoost~\cite{gehler2009feature}. In this method, a variant linear combination is applied to multiple classifiers to boost performance.
\end{itemize}

@@

In CIFAR-10 dataset, totally 60000 32x32 color pictures are categorized into 10 classes, with 6000 pictures per class.
There are 50000 training data and 10000 testing data.
Fourteen CNN features are extracted from multiple state of the art models.
This experiments exhibit the ability of our algorithm to handle large scale data.

As we have 50000 training data and 10000 testing data,
FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
LPBoost algorithm needs to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
\footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
which occupies too much memory and still consumes long time to train,
so we solve this problem by using sparse matrices and parallel computation in MATLAB.
We also use `-s 2' parameters in LIBLINEAR to speedup training process.
Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.
